MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-05-03 MAESTROeX_I/results.tex
paper updates
Updated wdconvect AMR results when refined tighter around the convective region

\section{Performance and Validation}

@@

Reacting bubble simulation at effective resolution of $128^2 \times 1024$ run on Cori Haswell with 48 processors took approximately 33.5 s per time step (averaged over 10 time steps) to run on single-level grid using either the original or new temporal algorithm, and only 3.7 s on adaptive grid with two levels of refinement. This 89\% decrease in runtime is mostly due to the fact that only 6.25\% of the cells (1,048,576 out of $128^2 \times 1024$ cells) are refined at the the finest level for the AMR run.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=3.5in]{./figs/wdconvect_amr_Tmax} 
\caption{\label{fig:wdconvect_amr_Tmax} Peak temperature, $T_{\text{peak}}$, in a white dwarf from $t=0$ to $350$ s 
         for grids with effective resolution of $512^3$. We can see that the adaptive grids with two levels of 
         refinement give very similar solution trends compared to the single-level grid.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Full white dwarf star simulation at effective resolution of $512^3$ on Cori KNL with 512 processors and 16 threads took 26.01 s per time step (averaged over 10 time steps) using the original temporal scheme, and 22.66 s using the new scheme. On an adaptive grid with two levels of refinement, the simulation took 34.69 s because the refinement region was set all the way to the edge of the star.

>>>>

\section{Performance and Validation}\label{sec:results}

@@

Reacting bubble simulation at effective resolution of $128^2 \times 1024$ run on Cori Haswell with 48 processors took approximately 33.5 s per time step (averaged over 10 time steps) to run on single-level grid using either the original or new temporal algorithm, and only 3.7 s on adaptive grid with two levels of refinement. This 89\% decrease in runtime is mostly due to the fact that only 6.25\% of the cells (1,048,576 out of $128^2 \times 1024$ cells) are refined at the finest level for the AMR run.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=4.0in]{./figs/wdconvect_amr_Tmax} 
\caption{\label{fig:wdconvect_amr_Tmax} Peak temperature, $T_{\text{peak}}$, in a white dwarf from $t=0$ to $400$ s 
         for grids with effective resolution of $512^3$. We can see that the adaptive grids with two levels of 
         refinement give very similar solution trends compared to the single-level grid.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Full white dwarf star simulation at effective resolution of $512^3$ on Cori KNL with 512 processors and 16 threads took 26.01 s per time step (averaged over 10 time steps) using the original temporal scheme, and 22.66 s using the new scheme. On an adaptive grid with two levels of refinement, 8.9\% of the cells (1,493,504 out of $256^3$ cells) are refined at the first level and 5.3\% (7,176,192 out of $512^3$ cells) at the second. The simulation took 11.55 s and 12.48 s using the orginial and new temporal schemes, respectively.
